### 2019-03-19 4_implementation.tex
More systems.

Spark~\cite{Spark10}

@@

StarPU~\cite{StarPU11}

@@

Swift/T~\cite{Wozniak13}

@@

TensorFlow~\cite{TensorFlow15}

@@

X10~\cite{X1005}

>>>>

Spark~\cite{Spark10} is an implicitly-parallel programming model for
data analytics, widely used in industrial data center applications. As
one of the programming models in this study not originally intended
for scientific computing, Spark makes very different tradeoffs from
other systems under consideration, and therefore makes an interesting
point of comparison.

Spark's programming model is based of \emph{functional parallelism}, a
generalization of the MapReduce programming
model~\cite{MapReduce04}. The core computational abstraction in Spark
are operators such as map, reduce, filter, join, etc. which by virtue
of being pure functions are trivially known to be
parallizable. Functions in Spark operate on \emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic, resulting in substantial speedups over MapReduce.

Though Spark has tasks internally, these are not exposed to the user,
so one of the challenges in developing a Task Bench implementation is
mapping the task graph to a set of operators which will result in the
desired performance behavior. We use a combination of
\lstinline[language=Scala]{flatMap} and
\lstinline[language=Scala]{groupByKey} operations to generate task
dependencies, and then \lstinline[language=Scala]{map} to execute a
series of tasks. We use an explicit hash partitioner to ensure that
Spark does not attempt to group multiple Task Bench tasks into a
single Spark task.

We performed an extensive set of experiments to verify that no
extraneous factors interfered with our Spark measurements. We
completely disabled logging, ensured that no RDDs are actually written
to disk, confirmed that there is no measurable overhead due to JNI
calls from Java to C, and cross-checked our results with known cases
that hit optimal task throughput in Spark, among other things. Our
results are discussed in detail in Section~\ref{sec:evaluation}.

@@

StarPU~\cite{StarPU11} is a task-based system that supports an STF
programming model similar to PaRSEC. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies, and manual
elision of tasks on unrelated nodes to provide horizontal scalability.

Internally, StarPU uses MPI for communication.

@@

Swift/T~\cite{Wozniak13} is a parallel scripting language intended
primarily for the composition of workflows in high-performance
scientific computing. Tasks in Swift/T can be written in any
programming language, and may even be themselves parallel. Swift/T
programs follow dataflow semantics, where every statement may
potentially execute in parallel as soon as its dependencies are
satisfied; statements only execute sequentially when explicitly
requested. The Swift/T compiler performs a number of optimizations to
improve performance of highly parallel programs~\cite{Armstrong14}.

Our Task Bench in Swift/T is straightforward, using Swift/T's dataflow
semantics to capture dependencies on other tasks.

Internally, Swift/T uses MPI for communication.

@@

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench and one of the shorter implementations at only 88 lines.

Our Task Bench implementation in TensorFlow works by defining a custom
operator, which represents the execution of one task. We then use
TensorFlow APIs to instantiate the custom operator for each point in
the task graph and connect the task dependencies with the TensorFlow
API.

@@

X10~\cite{X1005} is an explicitly parallel programming language for
place-based programming. The core features of X10 are \emph{places}
which represent distributed memories, a PGAS model where references to
remote objects can be held (but can only be deferenced on the local
place), asynchronous tasks, and a place-changing construct to move the
execution of a task to a remote place. X10 also supports a variety of
synchronization primitives.

Our Task Bench implementation uses
\lstinline[language=X10]{Rail.asyncCopy} for efficient data movement
between places, along with place-changing and atomic integers for
synchronization. We use the C++ backend of X10, which uses MPI
internally for portability to a variety of networks, and which
conveniently integrates well with the Task Bench API.
